Hierarchical Controller Architecture in Software Defined Networks

### 2013-12-16 paper/paper.tex
minor correction
ack

Results (Figure \ref{fig:timestamp}) shows that using timestamp could improve control application's performance. However, these are only preliminary results on a dummy topology and does not give any indication of the magnitude of improvement. We will evaluate timestamp optimization on a bigger topology with real world flow arrival data in the future.

@@

\section{Acknowledgements}
\label{sec:ack}
\nocite{*}

>>>>

Results (Figure \ref{fig:timestamp}) shows that using timestamp could improve control application's performance. However, these are only preliminary results on a dummy topology and does not give any indication of the magnitude of improvement. Going ahead, we plan to evaluate timestamp optimization on a bigger topology with real world flow arrival data.

@@

\section{Acknowledgements}
\label{sec:ack}
We would like to thank Prof. Brighten Godfrey and Prof. Matthew Caesar for their useful suggestions and support. 
\nocite{*}
